Raw Data Comparison

### 2019-10-09 Raw Data Comparison.Rmd
...

>>>>

# Adjusted to nearly integer ploidy?

files = list.files('~/Data/BarrettsProgressionRisk/Analysis/IntPloidy/multipcf_perPatient/', '5e06_tiled', recursive=T, full.names = T)
training.tiles.int = do.call(bind_rows, purrr::map(files, function(f) {
  read_tsv(f,col_types=c(.default=col_double()))
})) %>% dplyr::rename('Sample' = 'X1')

files = list.files('~/Data/BarrettsProgressionRisk/Analysis/IntPloidy/multipcf_perPatient/', 'arms_tiled', recursive=T, full.names = T)
training.arms.int = do.call(bind_rows, purrr::map(files, function(f) {
  read_tsv(f,col_types=c(.default=col_double()))
})) %>% dplyr::rename('Sample' = 'X1')

files = list.files('~/Data/BarrettsProgressionRisk/Analysis/validation/IntPloidy/', '5e06_cleaned_tiled', recursive=T, full.names = T)
val.tiles.int = do.call(bind_rows, purrr::map(files, function(f) {
  read_tsv(f,col_types=c(.default=col_double()))
})) %>% dplyr::rename('Sample' = 'X1')

files = list.files('~/Data/BarrettsProgressionRisk/Analysis/validation/IntPloidy/', 'arms_cleaned_tiled', recursive=T, full.names = T)
val.arms.int = do.call(bind_rows, purrr::map(files, function(f) {
  read_tsv(f,col_types=c(.default=col_double()))
})) %>% dplyr::rename('Sample' = 'X1')

t.pt = per.pt.tile(training.tiles.int) %>% mutate(cohort='train')
v.pt = per.pt.tile(val.tiles.int) %>% mutate(cohort='val')

gridExtra::grid.arrange(
  ggplot(bind_rows(t.pt, v.pt), aes(cohort, mean, group=cohort, fill=cohort)) + 
    geom_jitter(width=0.1) + geom_violin(alpha=0.5) + theme(legend.position = 'none') +
    labs(title='Mean per patient'),
  ggplot(bind_rows(t.pt, v.pt), aes(cohort, sd, group=cohort, fill=cohort)) + 
    geom_jitter(width=0.1) + geom_violin(alpha=0.5) + theme(legend.position = 'none') +
    labs(title='StdDev per patient'),
  ncol=2, top='Per patient tiled values')

mean(tile.dist.measure(training.tiles.int)$mean)
mean(tile.dist.measure(training.tiles.int)$sd)

mean(tile.dist.measure(val.tiles.int)$mean)
mean(tile.dist.measure(val.tiles.int)$sd)
